manuscript

### 2023-12-01 scripts/manuscript.qmd
good use of ggplot arguments

>>>>

I didn't know that `theme(legend.position = "none")` can omit the legend -- another thing I learned from your group! I have looked up  `scale_x_discrete()` before (but am not familiar with its use) and it's cool to see how you set the values for x scale aesthetics.

I also appreciate your naming conventions for each code chunk. This makes code editing and collaboration smoother.
